High-Dimensional Regularized Discriminant Analysis

### 2014-01-02 reports/paper-hdrda.Rnw
Added a couple of sentences describing how we handle the special case where (lambda, gamma) = (0, 0).

Notice that if $\alpha_k$ is constant across the $K$ classes, then $\bm
\Gamma_k$ in \eqref{eq:Gamma_k} is independent of $k$. Consequently, $|\bm
\Gamma_k|$ is constant across the $K$ classes and need not be calculated in
\eqref{eq:hdrda-decomposed}.

>>>>

The application of the Sherman-Woodbury formula requires that $\bm \Gamma_k$ be
nonsingular. This assumption is not met when $(\lambda, \gamma) = (0, 0)$ as
$\bm \Gamma_k = \bm 0_q$, corresponding to the \emph{QDA} classifier. In this
special case we apply a small amount of eigenvalue shrinkage and set $\gamma =
0.01$ to circumvent the singularity issue. Also, notice that if $\alpha_k$ is
constant across the $K$ classes, then $\bm \Gamma_k$ in \eqref{eq:Gamma_k} is
independent of $k$. Consequently, $|\bm \Gamma_k|$ is constant across the $K$
classes and need not be calculated in \eqref{eq:hdrda-decomposed}.
